\section{Conclusion and Future Work}
\label{sec:conclusion}

This study presented a comprehensive longitudinal analysis of the MyAnimeList ecosystem (2006–2018), offering a dual perspective on
the evolution of digital affinity networks: from the macroscopic topology of the graph to the microscopic dynamics of individual user migration.

Our findings challenge the assumption that expanding social networks necessarily become more cohesive. Instead, we observed a
\textbf{"Densification-Sparsification Paradox"}: while the user social graph densified into a "Small World," the content interest graph
expanded into a sparse "Metropolis" characterized by increasing taste divergence. This confirms that as the anime medium transitioned
from a niche subculture to a global entertainment force, the unified community fractured into distinct, self-reinforcing fandoms.

The methodological comparison of community detection algorithms identified the \textbf{Leiden algorithm} ($\gamma=1.0$) as the optimal
tool for longitudinal tracking, striking a balance between structural modularity and semantic interpretability. We demonstrated that "taste"
in this domain is a latent variable that correlates with, but is not synonymous with, explicit genre tags.

A critical contribution of this work is the evaluation of user navigation models. The stochastic Random Walker experiment yielded a negative
result of significant diagnostic value (similarity $\approx 4\%$), effectively disproving the hypothesis of "Topological Determinism."
Users do not passively flow down the gradients of the graph; their trajectories are driven by active, content-aware choices that defy
simple Markovian logic.

Consequently, we showed that user migration is a predictable phenomenon only when modeled as a complex interaction between structure and
behavior. The CatBoost classifier achieved high accuracy (ROC AUC 0.915), identifying the \textbf{Intra-Community Ratio (ICR)} as the
dominant predictor of stability. This suggests that the "social gravity" holding a user within a fandom is quantifiable and that migration
is preceded by a measurable decay in local ties.